---
title: "Analysis: External Debt"
output:
  rmdformats::html_clean:
    highlight: kate
code_folding: hide
---

# Preliminaries

Load libraries and pull macro data from the Word Bank.

```{r warning=FALSE, message=FALSE, error=FALSE, echo=FALSE}
library(stargazer)
library(plm)
library(dplyr)
library(WDI)

vars <- c("BN.CAB.XOKA.GD.ZS", "NY.GDP.PCAP.KD.ZG", "SL.TLF.CACT.ZS", "FP.CPI.TOTL.ZG")#, "GB.XPD.RSDV.GD.ZS")

form <- as.formula(paste("lhs ~", paste(vars, collapse="+")))

econ <- WDI(country = "all", indicator = vars, start = 1900, end = 2019)

econ$country <- toupper(econ$country)

```

## Load and scale mentions data.

```{r warning=FALSE, message=FALSE, error=FALSE, echo=FALSE}
recs <- read.csv("../rec_exp.txt", stringsAsFactors=FALSE, header=TRUE)
recs$Topic <- gsub(",", "", recs$Topic)
names(recs)[1]  <- "Country"

## calculate % mentions for each topic by country/year group------

recs <- recs %>%
    group_by(Country, Year) %>%
    mutate(lhs = Recommendations / sum(Recommendations))


recsED <- recs[recs$Topic == "External Debt", ]

## make sure each row is unique----

theIndex <- paste0(recsED$Country, "_", recsED$Year)

recsED <- cbind(theIndex, data.frame(recsED))
recsED$theIndex <- gsub(" ", "", recsED$theIndex)
rm(theIndex)


## Merge with IMF/WB Data-------

econ_vars_for_model <- econ[, c("country", "year", vars)]

## now need to extract only unique country and year subsets-----

theIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(theIndex, econ_vars_for_model)
rm(theIndex)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$theIndex))


#### Join data-----

mergedRecsED <- merge(recsED, econ_vars_for_model, by = "theIndex")

mergedRecsED <- mergedRecsED[, c("Country", "Year", "Recommendations", "lhs", vars)]

mergedRecsED <- mergedRecsED[complete.cases(mergedRecsED), ]

## convert to plm

mergedRecsED_p <- pdata.frame(mergedRecsED, index = c("Country", "Year"), drop.index=FALSE, row.names=TRUE)
```

#  Summary Statistics

The panel is unbalanced. 

# Analysis

## Model Estimation

```{r}
ols_recs <- lm(form, data = mergedRecsED_p)

pool_recs <- plm(form, data = mergedRecsED_p, model = "pooling")

FEestimate_recs <- plm(form, data = mergedRecsED_p, index = c("Country", "Year"), model = "within")

BEestimate_recs <- plm(form, data = mergedRecsED_p, index = c("Country", "Year"), model = "between")

REestimate_recs <- plm(form, data = mergedRecsED_p, index = c("Country", "Year"), model = "random")
```

## Test for Fixed versus Random Effects

Hausman test.

```{r}
phtest(FEestimate_recs, REestimate_recs)
```


## Test for Significant Fixed Effects

F-test.


```{r}
pFtest(FEestimate_recs, pool_recs)
```

Lagrange multiplier tests of individual effects.

## Within Estimator

We estimate the following 'within' model where:

$$y_{it} = {\bf x'_{it}}{\bf \beta} + \alpha_i + \epsilon_{it}$$

$y_i$ is the mentions/recommendations variable, and $x_i'$ is a vector of explanatory variables listed in "Variables to Include in Analysis" above.


```{r}
summary(FEestimate_recs)
```

## Between Estimator

We estimate the following 'between' model where:

$$\bar{y}_i=\alpha + \bar{x}_i' + (\alpha_i - \alpha + \bar{\epsilon}_i)$$

$y_i$ is the mentions/recommendations variable, and $x_i'$ is a vector of explanatory variables listed in "Variables to Include in Analysis" above.

```{r}
summary(BEestimate_recs)
```

## OLS Regressions

