
---
title: "Analysis: External Debt"
output:
  rmdformats::html_clean:
    highlight: kate
code_folding: hide
---

# Preliminaries

Load libraries and pull macro data from the word bank.

```{r warning=FALSE, message=FALSE, error=FALSE, echo=FALSE}
library(stargazer)
library(plm)
library(dplyr)
library(WDI)

vars <- c("BN.CAB.XOKA.GD.ZS", "NY.GDP.PCAP.KD.ZG", "SL.TLF.CACT.ZS", "FP.CPI.TOTL.ZG")#, "GB.XPD.RSDV.GD.ZS")

form <- as.formula(paste("lhs ~", paste(vars, collapse="+")))

econ <- WDI(country = "all", indicator = vars, start = 1900, end = 2019)

econ$country <- toupper(econ$country)

```

## Load and scale mentions data.

```{r warning=FALSE, message=FALSE, error=FALSE, echo=FALSE}
mentions <- read.csv("../raw_exp.txt", stringsAsFactors=FALSE, header=TRUE)
mentions$Topic <- gsub(",", "", mentions$Topic)
names(mentions)[1]  <- "Country"

## calculate % mentions for each topic by country/year group------

mentions <- mentions %>%
    group_by(Country, Year) %>%
    mutate(lhs = Mentions / sum(Mentions))

mentionsED <- mentions[mentions$Topic == "External Debt", ]

## make sure each row is unique----

mentionsEDindex <- paste0(mentionsED$Country, "_", mentionsED$Year)
mentionsEDindex <- gsub(" ", "", mentionsEDindex)

mentionsED <- cbind(mentionsEDindex, data.frame(mentionsED))

### Merge with IMF/WB Data

econ_vars_for_model <- econ[, c("country", "year", vars)]

## now need to extract only unique country and year subsets-----

econVarsIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(econVarsIndex, econ_vars_for_model)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$econVarsIndex))

#### Join data-----

mergedMentionsED <- merge(mentionsED, econ_vars_for_model, by.x = "mentionsEDindex", by.y = "econVarsIndex")

mergedMentionsED <- mergedMentionsED[, c("Country", "Year", "Mentions", "lhs", vars)]

mergedMentionsED <- mergedMentionsED[complete.cases(mergedMentionsED), ]

## convert to plm

mergedMentionsED_p <- pdata.frame(mergedMentionsED, index = c("Country", "Year"), drop.index=FALSE, row.names=TRUE)

```


# Analysis

## Model Estimation

```{r}
ols_mentions <- lm(form, data = mergedMentionsED_p)

pool_mentions <- plm(form, data = mergedMentionsED_p, model = "pooling")

FEestimate_mentions <- plm(form, data = mergedMentionsED_p, index = c("Country", "Year"), model = "within")

BEestimate_mentions <- plm(form, data = mergedMentionsED_p, index = c("Country", "Year"), model = "between")

REestimate_mentions <- plm(form, data = mergedMentionsED_p, index = c("Country", "Year"), model = "random")
```


## Test for Fixed versus Random Effects

Hausman test.


```{r}
phtest(FEestimate_mentions, REestimate_mentions)
```


## Test for Significant Fixed Effects

F-test vs pooled.

```{r}
pFtest(FEestimate_mentions, pool_mentions)
```

F-test vs ols.

```{r}
pFtest(FEestimate_mentions, ols_mentions)
```

<!-- Lagrange multiplier tests of individual effects. -->

## Test for Time Effects

```{r}
plmtest(FEestimate_mentions, c("time"), type = "bp")
```

The p-value is less than 0.05, so we should use time effects.

## Within Estimator

We estimate the following 'within' model where:

$$y_{it} = {\bf x'_{it}}{\bf \beta} + \alpha_i + \epsilon_{it}$$

$y_i$ is the mentions/recommendations variable, and $x_i'$ is a vector of explanatory variables listed in "Variables to Include in Analysis" above.


```{r}
summary(FEestimate_mentions)
```

## Within estimator with time effects.

```{r}
summary(plm(form, data = mergedMentionsED_p, index = c("Country", "Year"), model = "within", effects = "time"))
```


## Between Estimator

We estimate the following 'between' model where:

$$\bar{y}_i=\alpha + \bar{x}_i' + (\alpha_i - \alpha + \bar{\epsilon}_i)$$

$y_i$ is the mentions/recommendations variable, and $x_i'$ is a vector of explanatory variables listed in "Variables to Include in Analysis" above.

```{r}
summary(BEestimate_mentions)
```

## Between estimator with time effects

```{r}
summary(plm(form, data = mergedMentionsED_p, index = c("Country", "Year"), model = "between", effects = "time"))
```
