---
title: "Summary of Results"
date: "April 7, 2019"
output:
  rmdformats::html_clean:
    highlight: kate
code_folding: hide
---

```{r knitr_init, echo=FALSE, cache=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(rmdformats)
library(stargazer)
library(plm)
library(dplyr)

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	            cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```
# Model

Explanatory variables: 

#. Current account balance (% of GDP)(BN.CAB.XOKA.GD.ZS)
#. GDP per capita growth (annual %)(NY.GDP.PCAP.KD.ZG)

<!-- # Results Summary -->

<!-- ## External Debt -->

<!-- The signs of the coefficients make sense.  The number of recommendations/mentions is inversely related to the country's current account.   -->

# Next Steps?


#. Add explanatory variables.
#. Run for all topics.


# Count Results by Topic

## External Debt 

### Mentions

```{r results='asis'}
### pull and format mentions and recommendation data------

mentions <- read.csv("../../raw_exp.txt", stringsAsFactors=FALSE, header=TRUE)
mentions$Topic <- gsub(",", "", mentions$Topic)
names(mentions)[1]  <- "Country"

mentionsED <- mentions[mentions$Topic == "External Debt", ]

## make sure each row is unique----

mentionsEDindex <- paste0(mentionsED$Country, "_", mentionsED$Year)

mentionsED <- cbind(mentionsEDindex, mentionsED)
mentionsED$mentionsEDindex <- gsub(" ", "", mentionsED$mentionsEDindex)

## Merge with IMF/WB Data-------

econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

## now need to extract only unique country and year subsets-----

econVarsIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(econVarsIndex, econ_vars_for_model)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$econVarsIndex))


#### Join data-----

mergedMentionsED <- merge(mentionsED, econ_vars_for_model, by.x = "mentionsEDindex", by.y = "econVarsIndex")

mergedMentionsED <- mergedMentionsED[, c("Country", "Year", "Mentions", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

mergedMentionsED <- mergedMentionsED[complete.cases(mergedMentionsED), ]

## convert to plm

mergedMentionsED_p <- pdata.frame(mergedMentionsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(Mentions ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedMentionsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type="html")
```

### Recommendations


```{r results='asis'}
recs <- read.csv("../../rec_exp.txt", stringsAsFactors=FALSE, header=TRUE)
recs$Topic <- gsub(",", "", recs$Topic)
names(recs)[1]  <- "Country"

recsED <- recs[recs$Topic == "External Debt", ]

## make sure each row is unique----

theIndex <- paste0(recsED$Country, "_", recsED$Year)

recsED <- cbind(theIndex, recsED)
recsED$theIndex <- gsub(" ", "", recsED$theIndex)
rm(theIndex)


## Merge with IMF/WB Data-------

econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

## now need to extract only unique country and year subsets-----

theIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(theIndex, econ_vars_for_model)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$theIndex))


#### Join data-----

mergedRecsED <- merge(recsED, econ_vars_for_model, by = "theIndex")

mergedRecsED <- mergedRecsED[, c("Country", "Year", "Recommendations", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

mergedRecsED <- mergedRecsED[complete.cases(mergedRecsED), ]

mergedRecsED_p <- pdata.frame(mergedRecsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(Recommendations ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedRecsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type="html")


```

## Financial/Monetary

### Mentions

```{r results='asis'}
mentions <- read.csv("../../raw_exp.txt", stringsAsFactors=FALSE, header=TRUE)
mentions$Topic <- gsub(",", "", mentions$Topic)
names(mentions)[1]  <- "Country"

mentionsED <- mentions[mentions$Topic == "Financial/Monetary", ]

## make sure each row is unique----

mentionsEDindex <- paste0(mentionsED$Country, "_", mentionsED$Year)

mentionsED <- cbind(mentionsEDindex, mentionsED)
mentionsED$mentionsEDindex <- gsub(" ", "", mentionsED$mentionsEDindex)

## Merge with IMF/WB Data-------

econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

## now need to extract only unique country and year subsets-----

econVarsIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(econVarsIndex, econ_vars_for_model)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$econVarsIndex))

#### Join data-----

mergedMentionsED <- merge(mentionsED, econ_vars_for_model, by.x = "mentionsEDindex", by.y = "econVarsIndex")

mergedMentionsED <- mergedMentionsED[, c("Country", "Year", "Mentions", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

mergedMentionsED <- mergedMentionsED[complete.cases(mergedMentionsED), ]

## convert to plm

mergedMentionsED_p <- pdata.frame(mergedMentionsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(Mentions ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedMentionsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type="html")

```


### Recommendations


```{r results='asis'}
recs <- read.csv("../../rec_exp.txt", stringsAsFactors=FALSE, header=TRUE)
recs$Topic <- gsub(",", "", recs$Topic)
names(recs)[1]  <- "Country"

recsED <- recs[recs$Topic == "Financial/Monetary", ]

## make sure each row is unique----

theIndex <- paste0(recsED$Country, "_", recsED$Year)

recsED <- cbind(theIndex, recsED)
recsED$theIndex <- gsub(" ", "", recsED$theIndex)
rm(theIndex)

## Merge with IMF/WB Data-------

econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

## now need to extract only unique country and year subsets-----

theIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(theIndex, econ_vars_for_model)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$theIndex))


#### Join data-----

mergedRecsED <- merge(recsED, econ_vars_for_model, by = "theIndex")

mergedRecsED <- mergedRecsED[, c("Country", "Year", "Recommendations", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

mergedRecsED <- mergedRecsED[complete.cases(mergedRecsED), ]

## convert to plm

mergedRecsED_p <- pdata.frame(mergedRecsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(Recommendations ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedRecsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type="html")

```

# Scaled Results by Topic

## External Debt

### Scaled Mentions

```{r results='asis'}

### pull and format mentions and recommendation data------

mentions <- read.csv("../../raw_exp.txt", stringsAsFactors=FALSE, header=TRUE)
mentions$Topic <- gsub(",", "", mentions$Topic)
names(mentions)[1]  <- "Country"

## calculate % mentions for each topic by country/year group------

mentions <- mentions %>%
    group_by(Country, Year) %>%
    mutate(scaled = Mentions / sum(Mentions))

mentionsED <- mentions[mentions$Topic == "External Debt", ]

## make sure each row is unique----

mentionsEDindex <- paste0(mentionsED$Country, "_", mentionsED$Year)
mentionsEDindex <- gsub(" ", "", mentionsEDindex)

mentionsED <- cbind(mentionsEDindex, data.frame(mentionsED))

## Merge with IMF/WB Data-------

econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

## now need to extract only unique country and year subsets-----

econVarsIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(econVarsIndex, econ_vars_for_model)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$econVarsIndex))


#### Join data-----

mergedMentionsED <- merge(mentionsED, econ_vars_for_model, by.x = "mentionsEDindex", by.y = "econVarsIndex")

mergedMentionsED <- mergedMentionsED[, c("Country", "Year", "Mentions", "scaled", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

mergedMentionsED <- mergedMentionsED[complete.cases(mergedMentionsED), ]

## convert to plm

mergedMentionsED_p <- pdata.frame(mergedMentionsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(scaled ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedMentionsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type="html")

```
### Scaled Recommendations

```{r results='asis', warnings=FALSE, message=FALSE}

recs <- read.csv("../../rec_exp.txt", stringsAsFactors=FALSE, header=TRUE)
recs$Topic <- gsub(",", "", recs$Topic)
names(recs)[1]  <- "Country"

## calculate % mentions for each topic by country/year group------

recs <- recs %>%
    group_by(Country, Year) %>%
    mutate(scaled = Recommendations / sum(Recommendations))


recsED <- recs[recs$Topic == "External Debt", ]

## make sure each row is unique----

theIndex <- paste0(recsED$Country, "_", recsED$Year)

recsED <- cbind(theIndex, data.frame(recsED))
recsED$theIndex <- gsub(" ", "", recsED$theIndex)
rm(theIndex)


## Merge with IMF/WB Data-------


econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

## now need to extract only unique country and year subsets-----

theIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(theIndex, econ_vars_for_model)
rm(theIndex)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$theIndex))


#### Join data-----

mergedRecsED <- merge(recsED, econ_vars_for_model, by = "theIndex")

mergedRecsED <- mergedRecsED[, c("Country", "Year", "Recommendations", "scaled", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

mergedRecsED <- mergedRecsED[complete.cases(mergedRecsED), ]

## convert to plm

mergedRecsED_p <- pdata.frame(mergedRecsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(scaled ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedRecsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type="html")

```
## Financial/Monetary

### Scaled Mentions

```{r results='asis', warnings=FALSE, message=FALSE}

### pull and format mentions and recommendation data------

mentions <- read.csv("../../raw_exp.txt", stringsAsFactors=FALSE, header=TRUE)
mentions$Topic <- gsub(",", "", mentions$Topic)
names(mentions)[1]  <- "Country"

## calculate % mentions for each topic by country/year group------

library(dplyr)

mentions <- mentions %>%
    group_by(Country, Year) %>%
    mutate(scaled = Mentions / sum(Mentions))

mentionsED <- mentions[mentions$Topic == "Financial/Monetary", ]

## make sure each row is unique----

mentionsEDindex <- paste0(mentionsED$Country, "_", mentionsED$Year)
mentionsEDindex <- gsub(" ", "", mentionsEDindex)

mentionsED <- cbind(mentionsEDindex, data.frame(mentionsED))

## Merge with IMF/WB Data-------

econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

## now need to extract only unique country and year subsets-----

econVarsIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(econVarsIndex, econ_vars_for_model)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$econVarsIndex))

#### Join data-----

mergedMentionsED <- merge(mentionsED, econ_vars_for_model, by.x = "mentionsEDindex", by.y = "econVarsIndex")

mergedMentionsED <- mergedMentionsED[, c("Country", "Year", "Mentions", "scaled", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

mergedMentionsED <- mergedMentionsED[complete.cases(mergedMentionsED), ]

## convert to plm

mergedMentionsED_p <- pdata.frame(mergedMentionsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(scaled ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedMentionsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type = "html")

```

### Scaled Recommendations

```{r results='asis', warnings=FALSE, message=FALSE}

recs <- read.csv("../../rec_exp.txt", stringsAsFactors=FALSE, header=TRUE)
recs$Topic <- gsub(",", "", recs$Topic)
names(recs)[1]  <- "Country"

## calculate % mentions for each topic by country/year group------

library(dplyr)

recs <- recs %>%
    group_by(Country, Year) %>%
    mutate(scaled = Recommendations / sum(Recommendations))


recsED <- recs[recs$Topic == "Financial/Monetary", ]

## make sure each row is unique----

theIndex <- paste0(recsED$Country, "_", recsED$Year)

recsED <- cbind(theIndex, data.frame(recsED))
recsED$theIndex <- gsub(" ", "", recsED$theIndex)
rm(theIndex)


## Merge with IMF/WB Data-------

econ <- read.csv("../../../pulling_data/merged_data.csv", stringsAsFactors=FALSE, header=TRUE)

econ_vars_for_model <- econ[, c("country", "year", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG", "IC.FRM.BNKS.ZS")]

## now need to extract only unique country and year subsets-----

theIndex <- paste0(econ_vars_for_model$country, "_", econ_vars_for_model$year)

econ_vars_for_model <- cbind(theIndex, econ_vars_for_model)
rm(theIndex)

econ_vars_for_model <- subset(econ_vars_for_model, !duplicated(econ_vars_for_model$theIndex))


#### Join data-----

mergedRecsED <- merge(recsED, econ_vars_for_model, by = "theIndex")

mergedRecsED <- mergedRecsED[, c("Country", "Year", "Recommendations", "scaled", "BN.CAB.XOKA.GD.ZS.x", "NY.GDP.PCAP.KD.ZG")]

mergedRecsED <- mergedRecsED[complete.cases(mergedRecsED), ]

## convert to plm

mergedRecsED_p <- pdata.frame(mergedRecsED, index = c("Country", "Year"), drop.index=TRUE, row.names=TRUE)

FEestimate <- plm(scaled ~  BN.CAB.XOKA.GD.ZS.x + NY.GDP.PCAP.KD.ZG, data = mergedRecsED_p, model = "between", effect = "individual")

stargazer(FEestimate, type = "html")

```
